Certified Knowledge Compilation \\ with Application to Formally Verified Model Counting

### 2024-01-06 doc/JAIR/jair-paper.tex
fix: typo

Suppose for every clause $C_j \in \gamma_{\nodeu}$ that does not correspond to
an input clause, we generate a synthetic clause $C'_j$ with guard literal
$\obar{v}_j$, for $1 \leq j \leq m$.  Let $\gamma'_{\nodeu}$ be the formula where each clause $C_j$ is replaced by synthetic clause $C'_j$,
while input clauses in $\gamma_{\nodeu}$ are left unchanged.
Let $\lassign = \{ \obar{v}_1, \obar{v}_2, \ldots, \obar{v}_m \}$.
Invoking $\validate(\nodeu, \lassign, \gamma'_{\nodeu})$
 will then prove a lemma, given by the target clause
 $u \lor v_1 \lor v_2 \lor \cdots \lor v_m$,
 showing that any total assignment $\assign$ that activates the synthetic clauses will, when cause $u$ to be assigned $1$.
 More precisely, given assignment $\assign$ and its extension $\eassign$, if $\eassign(v_j) = 0$ for every guard literal $\obar{v}_j$, then $\eassign(u) = 1$.

>>>>

Suppose for every clause $C_j \in \gamma_{\nodeu}$ that does not correspond to
an input clause, we generate a synthetic clause $C'_j$ with guard literal
$\obar{v}_j$, for $1 \leq j \leq m$.  Let $\gamma'_{\nodeu}$ be the formula where each clause $C_j$ is replaced by synthetic clause $C'_j$,
while input clauses in $\gamma_{\nodeu}$ are left unchanged.
Let $\lassign = \{ \obar{v}_1, \obar{v}_2, \ldots, \obar{v}_m \}$.
Invoking $\validate(\nodeu, \lassign, \gamma'_{\nodeu})$
 will then prove a lemma, given by the target clause
 $u \lor v_1 \lor v_2 \lor \cdots \lor v_m$,
 showing that any total assignment $\assign$ that activates the synthetic clauses will cause $u$ to be assigned $1$.
 More precisely, given assignment $\assign$ and its extension $\eassign$, if $\eassign(v_j) = 0$ for every guard literal $\obar{v}_j$, then $\eassign(u) = 1$.
